Supplemental Information: Aligning marine species range data to better serve science and conservation

### 2016-09-11 ms_6_supplemental.Rmd
updated refs for supplemental

__Fig S1.__  Examples of AquaMaps and IUCN raw species range data. (A, B) AquaMaps distribution of _Thunnus alalunga_ (Albacore Tuna) [@kaschner_aquamaps:_2015] showing global range with varying probabilities of occurrence assigned to 0.5° grid cells (A) and presence within 0.5° grid cells (B). (C, D) IUCN distribution of _T. alalunga_ [@@iucn_iucn_2015] represented as extent of occurrence polygons (C) and presence within 0.5° grid cells (D).

@@

__Fig S3.__ Representative species maps [@kaschner_aquamaps:_2015; @iucn_iucn_2015] to illustrate each quadrant from Fig 2A.  Each map is positioned to match its quadrant in Fig 2A.
(A) Distribution-matched: _Conus episcopatus_, the dignified cone snail.  Distributions show excellent overlap in the western Pacific, though IUCN range extends well beyond the bounds of the AquaMaps range.
(B) Well-matched: _Kajikia albida_, the Atlantic white marlin.  Distributions from each data set show nearly complete overlap, and very similar range size.
(C) Poorly-matched: _Acanthurus nigroris_, the blue-lined surgeonfish.  IUCN predicts species distribution only near the Hawaiian islands; AquaMaps predicts extensive distribution throughout the central and western Pacific Ocean.  The datasets align in neither distribution nor range size.
(D) Area-matched: _Conus magnificus_, the magnificent cone snail.  Distributions overlap in the southern Pacific, but align poorly elsewhere.  The range sizes are similar.

@@

>>>>

__Fig S1.__  Examples of AquaMaps and IUCN raw species range data. (A, B) AquaMaps distribution of _Thunnus alalunga_ (Albacore Tuna) (AquaMaps 2013e) showing global range with varying probabilities of occurrence assigned to 0.5° grid cells (A) and presence within 0.5° grid cells (B). (C, D) IUCN distribution of _T. alalunga_ (IUCN 2011b) represented as extent of occurrence polygons (C) and presence within 0.5° grid cells (D).

@@

__Fig S3.__ Representative species maps (AquaMaps 2013abcd; Conch 2013ab; IUCN 2011a; IUCN 2012) to illustrate each quadrant from Fig 2A.  Each map is positioned to match its quadrant in Fig 2A.
(A) Distribution-matched: _Conus episcopatus_, the dignified cone snail.  Distributions show excellent overlap in the western Pacific, though IUCN range extends well beyond the bounds of the AquaMaps range.
(B) Well-matched: _Kajikia albida_, the Atlantic white marlin.  Distributions from each data set show nearly complete overlap, and very similar range size.
(C) Poorly-matched: _Acanthurus nigroris_, the blue-lined surgeonfish.  IUCN predicts species distribution only near the Hawaiian islands; AquaMaps predicts extensive distribution throughout the central and western Pacific Ocean.  The datasets align in neither distribution nor range size.
(D) Area-matched: _Conus magnificus_, the magnificent cone snail.  Distributions overlap in the southern Pacific, but align poorly elsewhere.  The range sizes are similar.

@@

## References for supplemental information

Conch Books, Hackenheim, Germany 2013. Conus episcopatus. The IUCN Red List of Threatened Species. Version 2016-2

Conch Books, Hackenheim, Germany 2013. Conus magnificus. The IUCN Red List of Threatened Species. Version 2016-2

International Union for Conservation of Nature (IUCN) 2011. Kajikia albida. The IUCN Red List of Threatened Species. Version 2016-2

International Union for Conservation of Nature (IUCN) 2011. Thunnus alalunga. The IUCN Red List of Threatened Species. Version 2016-2

International Union for Conservation of Nature (IUCN) 2012. Acanthurus nigroris. The IUCN Red List of Threatened Species. Version 2016-2

www.aquamaps.org, version of Aug. 2013. Computer generated distribution maps for Conus episcopatus, with modelled year 2100 native range map based on IPCC A2 emissions scenario. Web. Accessed 11 Sep. 2016.

www.aquamaps.org, version of Aug. 2013. Computer generated distribution maps for Conus magnificus, with modelled year 2100 native range map based on IPCC A2 emissions scenario. Web. Accessed 11 Sep. 2016.

www.aquamaps.org, version of Aug. 2013. Computer generated distribution maps for Kajikia albida (Atlantic white marlin), with modelled year 2100 native range map based on IPCC A2 emissions scenario. Web. Accessed 11 Sep. 2016.

www.aquamaps.org, version of Aug. 2013. Reviewed distribution maps for Acanthurus nigroris (Bluelined surgeonfish), with modelled year 2100 native range map based on IPCC A2 emissions scenario. Web. Accessed 11 Sep. 2016.

www.aquamaps.org, version of Aug. 2013. Reviewed distribution maps for Thunnus alalunga (Albacore), with modelled year 2100 native range map based on IPCC A2 emissions scenario. Web. Accessed 11 Sep. 2016.
